
\item Chromatin structure and organization in transcription, DNA replication, and repair.   

The local chromatin environment regulates almost all genomic activity including transcription, replication and repair.  We have developed a factor agnostic approach to footprint  protein occupancy on DNA at nucleotide resolution throughout the yeast genome.  This approach provides a holistic and unbiased view of chromatin dynamics at individual loci throughout the genome.  We have used this methodology to characterize origin specific chromatin dynamics during helicase loading\textsuperscript{a} and activation\textsuperscript{b}. We have also developed predictive models of gene expression from the chromatin dynamics associated with exposure to environmental stress\textsuperscript{c}. Finally, we have described the chromatin dynamics that occur following a site specific DNA double strand break and its subsequent repair by non-homologous end joining\textsuperscript{d}.  Together, these studies have provided mechanistic insight into how the local chromatin environment influences a variety of genome activities.  

%the seand activation   a at nucleoMuch progress over the last decade has been made in our understanding of how the local chromatin environment regulates the transcription program.  In contrast, we know comparatively little about how the DNA replication program is regulated by the chromatin landscape.  Our recent work has been focused on understanding how the local chromatin organization impacts the selection and activation of eukaryotic DNA replication origins.  We have found that nucleosome positioning\textsuperscript{a} and nucleosome remodeling\textsuperscript{b,c} at the origin are key determinants regulating the selection and activation of eukaryotic origins.  

\begin{enumerate}
\setlength\itemsep{0.35em}


\item Belsky JA, MacAlpine HK, Lubelsky Y, Hartemink AJ, \textbf{MacAlpine DM}. Genome-wide chromatin footprinting reveals changes in replication origin architecture induced by pre-RC assembly. Genes Dev. 2015 Jan 15;29(2):212-24. PMC4298139.

\item Hoffman RA, MacAlpine HK, \textbf{MacAlpine DM}. Disruption of origin chromatin structure by helicase activation in the absence of DNA replication. Genes Dev. 2021 Oct 1;35(19-20):1339-1355. doi: 10.1101/gad.348517.121. Epub 2021 Sep 23. PMC8494203.

\item Tran TQ, MacAlpine HK, Tripuraneni V, Mitra S, \textbf{MacAlpine DM}, Hartemink AJ. Linking the dynamics of chromatin occupancy and transcription with predictive models. Genome Res. 2021 Jun;31(6):1035-1046. doi: 10.1101/gr.267237.120. Epub 2021 Apr 23. PMC8168580.

\item Tripuraneni V, Memisoglu G, MacAlpine HK, Tran TQ, Zhu W, Hartemink AJ, Haber JE, \textbf{MacAlpine DM}. Local nucleosome dynamics and eviction following a double-strand break are reversible by NHEJ-mediated repair in the absence of DNA replication. Genome Res. 2021 May;31(5):775-788. doi: 10.1101/gr.271155.120. Epub 2021 Apr 2. PMC8092003.

\end{enumerate}
