
\item Collaborative work

\noindent A hallmark of my scientific career has been my willingness to collaborate on a diverse array of projects.  We have been delighted to share our expertise in DNA replication, genomics and computational biology with multiple collaborators.  Recent replication focused collaborations include characterizing the role of DNA methylation and heterochromatin in recruiting ORCA/LRWD1 to mammalian replication origins\textsuperscript{a} with Supriya Prasanth and the transcription-dependent displacement of the Mcm2-7 complex in the rDNA of yeast\textsuperscript{b} with Antonio Bedalov.  In collaboration with Robert Duronio, we used genetically engineered histone mutants to perturb constitutive heterochromatin in order to study the impact on the transcription and DNA replication programs\textsuperscript{c}.  Together with Chris Counter, we have been able to apply our molecular biology and computational expertise to develop and extend maximum depth sequencing to identify rare initiating RAS mutations following urethane mutagenesis\textsuperscript{d}.  



\begin{enumerate}
\setlength\itemsep{0.35em}


\item Wang Y, Khan A, Marks AB, Smith OK, Giri S, Lin YC, Creager R, \textbf{MacAlpine DM},
Prasanth KV, Aladjem MI, Prasanth SG. Temporal association of ORCA/LRWD1 to
late-firing origins during G1 dictates heterochromatin replication and
organization. Nucleic Acids Res. 2016 Dec 6. PMC5389698.


\item Foss EJ, Gatbonton-Schwager T, Thiesen AH, Taylor E, Soriano R, Lao U, \textbf{MacAlpine DM}, Bedalov A. Sir2 suppresses transcription-mediated displacement of Mcm2-7 replicative helicases at the ribosomal DNA repeats. PLoS Genet. 2019 May 13;15(5):e1008138. doi: 10.1371/journal.pgen.1008138. PMID: 31083663; PMC6532929.

\item Armstrong RL, Penke TJR, Strahl BD, Matera AG, McKay DJ, \textbf{MacAlpine DM}, Duronio RJ. Chromatin conformation and transcriptional activity are permissive regulators of DNA replication initiation in Drosophila. Genome Res. 2018 Nov;28(11):1688-1700. doi: 10.1101/gr.239913.118. Epub 2018 Oct 2. PMID: 30279224; PMC6211642.


\item Li S, \textbf{MacAlpine DM,} Counter CM. Capturing the primordial Kras mutation initiating urethane carcinogenesis. Nat Commun. 2020 Apr 14;11(1):1800. doi: 10.1038/s41467-020-15660-8. PMC7156420.

\end{enumerate}

