\item Establishment and maintenance of the \dros DNA replication program

In higher eukaryotes, there is little apparent sequence specificity for ORC and the identification of conserved cis-acting elements that direct origin function has remained elusive.  My research program has used \dros to identify the epigenetic determinants of origin selection and function. We have identified activating chromatin marks, nucleosome occupancy, and ATP-dependent chromatin remodelers as being predictive features of ORC binding and origin activation\textsuperscript{a}. We also found that transcription and DNA replication respond to the same chromatin states.  For example, male specific H4K16 hyperacetylation up-regulates transcription and promotes the early replication of the X-chromosome\textsuperscript{b}.  Unlike in mammalian systems, we found that the cell cycle regulated H4K20 monomethylation did not promote helicase loading and origin activation, but rather was essential for maintaining the genomic integrity of late replicating regions of the \dros\ genome\textsuperscript{c}.  Finally, recent work on the loading and distribution of the Mcm2-7 complex revealed that transcription can shape the distribution of the Mcm2-7 complex in late G1, thus providing a possible mechanism(s) for the apparent stochastic activation of replication origins throughout the genomes of higher eukaryotes\textsuperscript{d}.


\begin{enumerate}
\setlength\itemsep{0.35em}

\item Eaton ML, Prinz JA, MacAlpine HK, Tretyakov G, Kharchenko PV, \textbf{MacAlpine DM}. Chromatin signatures of the Drosophila replication program. Genome Res. 2011 Feb;21(2):164-74. PMC3032920.

\item Lubelsky Y, Prinz JA, DeNapoli L, Li Y, Belsky JA, \textbf{MacAlpine DM}. DNA
replication and transcription programs respond to the same chromatin cues. Genome Res. 2014 Jul;24(7):1102-14. PMC4079966.

\item Li Y, Armstrong RL, Duronio RJ, \textbf{MacAlpine DM}. Methylation of histone H4 lysine 20 by PR-Set7 ensures the integrity of late replicating sequence domains in Drosophila. Nucleic Acids Res. 2016 Sep 6;44(15):7204-18.  Epub 2016 Apr 29. PMC5009726.

\item Powell SK, MacAlpine HK, Prinz JA, Li Y, Belsky JA, \textbf{MacAlpine DM}. Dynamic
loading and redistribution of the Mcm2-7 helicase complex through the cell cycle. EMBO J. 2015 Feb 12;34(4):531-43. Epub 2015 Jan 2. PMC4331006.


\end{enumerate}
